|

### 2021-02-14 supplementary_information.Rmd
edits: sourced tables

---
title: |
  | Supplementary Information for:
  | Ecosystem size and complexity dictate riverine biodiversity
author:
- Akira Terui^[Department of Biology, University of North Carolina at Greensboro]
- Seoghyun Kim\footnotemark[1]
- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of
  Minnesota]
- Taku Kadoya^[National Institute for Environmental Studies]
- Yusuke Miyazaki^[Shiraume Gakuen University]
output:
  pdf_document:
    toc: yes
    toc_depth: 2
bibliography: reference.bib
csl: nature.csl
---

@@

  # simulation data main
  dat_sim <- read_csv(here::here('/theory/result/result_sim2020-11-10.csv'))

  # sensitivity analysis  
  source(here::here("/theory/analysis_sensitivity.R"))

@@

  # sensitivity tables

  ## ecosystem size
  m_area <- fit_sense %>% 
    mutate(area = str_detect(response, "area")) %>% 
    filter(area == TRUE)

  star_area <- stargazer::stargazer(m_area$fit[1],
                                    m_area$fit[2],
                                    m_area$fit[3],
                                    header = FALSE,
                                    type = "latex",
                                    covariate.labels = c("$\\sigma_{h}$",
                                                         "$\\sigma_{l}$",
                                                         "$\\sigma_{z}$",
                                                         "$\\phi$",
                                                         "$\\nu$",
                                                         "$\\alpha_{max}$",
                                                         "$\\theta$",
                                                         "$p_{d}$",
                                                         "Intercept"),
                                    single.row = FALSE,
                                    digits = 3,
                                    dep.var.caption  = "Response variable",
                                    dep.var.labels.include = FALSE,
                                    column.labels = c("Effect of $N_{p}$ on $\\alpha$ diversity",
                                                      "Effect of $N_{p}$ on $\\beta$ diversity",
                                                      "Effect of $N_{p}$ on $\\gamma$ diversity"),
                                    report = "vcs",
                                    omit.table.layout = "ns",
                                    model.numbers = FALSE)

  star_area <- sub('^.+\\caption.+$','', star_area)

  ## Ecosystem complexity
  m_bp <- fit_sense %>% 
    mutate(area = str_detect(response, "area")) %>% 
    filter(area == FALSE)

  star_bp <- stargazer::stargazer(m_bp$fit[1],
                                  m_bp$fit[2],
                                  m_bp$fit[3],
                                  header = FALSE,
                                  type = "latex",
                                  covariate.labels = c("$\\sigma_{h}$",
                                                       "$\\sigma_{l}$",
                                                       "$\\sigma_{z}$",
                                                       "$\\phi$",
                                                       "$\\nu$",
                                                       "$\\alpha_{max}$",
                                                       "$\\theta$",
                                                       "$p_{d}$",
                                                       "Intercept"),
                                  single.row = FALSE,
                                  digits = 3,
                                  dep.var.caption  = "Response variable",
                                  dep.var.labels.include = FALSE,
                                  column.labels = c("Effect of $P_{b}$ on $\\alpha$ diversity",
                                                    "Effect of $P_{b}$ on $\\beta$ diversity",
                                                    "Effect of $P_{b}$ on $\\gamma$ diversity"),
                                  report = "vcs",
                                  omit.table.layout = "ns",
                                  model.numbers = FALSE)

    star_bp <- sub('^.+\\caption.+$','', star_bp)

@@

  tibble(Parameter = c('$\\sigma_{h}$',
                       '$\\sigma_{l}$',
                       '$\\sigma_{z}$',
                       '$\\rho$',
                       '$\\phi$',
                       '$\\nu$',
                       '$\\alpha_{max}$',
                       '$\\theta$',
                       '$p_{d}$',
                       '$r_{0,i}$'),
         Value = c('Unif(0.01, 1)',
                   'Unif(0.01, 1)',
                   'Unif(0.01, 0.5)',
                   '1',
                   'Unif(0.01, 1)',
                   'Unif(1, 5)',
                   'Unif(0.5, 1.5)',
                   'Unif(0.1, 1)',
                   'Unif(0.01, 0.1)',
                   '4'),
         Interpretation = c('Environmental variation at headwaters',
                            'Degree of local environmental noise',
                            'Temporal environmental variability',
                            'Strength of spatial autocorrelation in mean environmental condition',
                            'Extent of spatial autocorrelation in temporal environmental variation',
                            'Cost of a wider niche',
                            'Maximum value of interspecific competition coefficient',
                            'Rate parameter of an exponential dispersal kernel',
                            'Dispersal probability',
                            'Maximum reproductive rate')) %>% 
    kable(format = 'markdown')

@@

  dat_sim %>% 
    select(sd_env_source,
           sd_env_lon,
           sd_env,
           rho,
           phi,
           niche_cost,
           max_alpha,
           theta,
           p_dispersal
    ) %>% 
    summarise(across(everything(), unique)) %>% 
    mutate(r0 = 4) %>% 
    pivot_longer(cols = everything(),
                 names_to = "Parameter",
                 values_to = "Value") %>% 
    group_by(Parameter) %>% 
    summarize(Value = list(unique(Value))) %>% 
    mutate(id = case_when(Parameter == 'sd_env_source' ~ 'a',
                          Parameter == 'sd_env_lon' ~ 'b',
                          Parameter == 'sd_env' ~ 'c',
                          Parameter == 'rho' ~ 'd',
                          Parameter == 'phi' ~ 'e',
                          Parameter == 'niche_cost' ~ 'f',
                          Parameter == 'max_alpha' ~ 'g',
                          Parameter == 'theta' ~ 'h',
                          Parameter == 'p_dispersal' ~ 'i',
                          Parameter == 'r0' ~ 'j',
                          TRUE ~ as.character(Parameter)),
           Interpretation = case_when(Parameter == 'sd_env_source' ~ 'Environmental variation at headwaters',
                                      Parameter == 'sd_env_lon' ~ 'Degree of local environmental noise',
                                      Parameter == 'sd_env' ~ 'Temporal environmental variability',
                                      Parameter == 'rho' ~ 'Strength of spatial autocorrelation in mean environmental condition',
                                      Parameter == 'phi' ~ 'Extent of spatial autocorrelation in temporal environmental variation',
                                      Parameter == 'niche_cost' ~ 'Cost of a wider niche',
                                      Parameter == 'max_alpha' ~ 'Maximum value of interspecific competition coefficient',
                                      Parameter == 'theta' ~ 'Rate parameter of an exponential dispersal kernel',
                                      Parameter == 'p_dispersal' ~ 'Dispersal probability',
                                      Parameter == 'r0' ~ 'Maxiumum reproductive rate',
                                      TRUE ~ as.character(Parameter)),
           Parameter = case_when(Parameter == 'sd_env_source' ~ '$\\sigma_{h}$',
                                 Parameter == 'sd_env_lon' ~ '$\\sigma_{l}$',
                                 Parameter == 'sd_env' ~ '$\\sigma_{z}$',
                                 Parameter == 'rho' ~ '$\\rho$',
                                 Parameter == 'phi' ~ '$\\phi$',
                                 Parameter == 'niche_cost' ~ '$\\nu$',
                                 Parameter == 'max_alpha' ~ '$\\alpha_{max}$',
                                 Parameter == 'theta' ~ '$\\theta$',
                                 Parameter == 'p_dispersal' ~ '$p_{d}$',
                                 Parameter == 'r0' ~ '$r_{0,i}$',
                                 TRUE ~ as.character(Parameter))
    ) %>% 
    arrange(id) %>% 
    select(-id) %>% 
    kable(format = 'markdown')

@@

dat_hkd %>% 
    mutate(n_site = n_distinct(SiteID)) %>% 
    mutate(Species = str_replace_all(str_to_title(Species), "_", " ")) %>% 
    mutate(Species = str_replace_all(Species, "(spp$)|(spp\\s)", "spp\\.")) %>% 
    mutate(Species = str_replace_all(Species, "(sp$)", "sp\\.")) %>% 
    mutate(Species = str_replace_all(Species, "(subsp)", "subsp\\. ")) %>% 
    mutate(Species = str_replace_all(Species, "(sp\\sme$)", "sp\\. ME")) %>% 
    group_by(Species) %>% 
    summarise('Number of sites present' = n_distinct(SiteID),
              'Occupancy (%)' = round((n_distinct(SiteID)*100)/unique(n_site), 2)) %>% 
    kable(format = 'markdown')

@@

sp_mw_latin <- read_csv(here::here('/empirical/data_out/data_mw_splist_latin.csv'))

  dat_mw %>% 
    mutate(n_site = n_distinct(SiteID)) %>% 
    rename(Common_name = Species) %>% 
    group_by(Common_name) %>% 
    summarise('Number of sites present' = n_distinct(SiteID),
              'Occupancy (%)' = round((n_distinct(SiteID)*100)/unique(n_site), 2)) %>% 
    left_join(sp_mw_latin, by = "Common_name") %>% 
    select(Species = Latin_name,
           'Number of sites present',
           'Occupancy (%)') %>% 
    arrange(Species) %>% 
    kable(format = 'markdown')

>>>>

---
title: |
  | Supplementary Information for:
  | Ecosystem size and complexity dictate riverine biodiversity
author:
- Akira Terui^[Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA]
- Seoghyun Kim\footnotemark[1]
- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of
  Minnesota, St. Paul, MN 55108, USA]
- Taku Kadoya^[National Institute for Environmental Studies, Tsukuba, Ibaraki 305-8506, Japan]
- Yusuke Miyazaki^[Shiraume Gakuen College, Kodaira, Tokyo 187-8570, Japan]
output:
  pdf_document:
    toc: yes
    toc_depth: 2
bibliography: reference.bib
csl: nature.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

@@

@@

  # sensitivity tables
  source(here::here('theory/table_sensitivity_analysis.R'))

@@

  source(here::here('empirical/table_sim_parameter_sensitivity.R'))
  table_output

@@

  source(here::here('empirical/table_sim_parameter_main.R'))
  table_output

@@

  source(here::here('empirical/table_splist_hkd.R'))
  table_output

@@

  source(here::here('empirical/table_splist_mw.R'))
  table_output
